beautier: BEAUti for R

### 2017-12-19 article.tex
beautier in verbatim

BEAST2 \cite{bouckaert2014beast} is a popular Bayesian phylogenetics tool.
BEAST2 is bundled with the program called BEAUti \cite{drummond2012bayesian},
which  allows for a user-friendly way to create the
input files that BEAST2 needs. BEAUti is convenient to get started, yet
does not allow for the scripted use of BEAST2. For creating BEAST2 input
files from a script, beautier is the R package facilitating this:
it creates a BEAST2 input files from an R function call.

@@

By creating BEAST2 input files in BEAUti, 
the desired output of beautier was determined. 
The functionality of BEAUti is added gradually (and is still growing).

@@

Novel about beautier is that it allows for specifying a fixed crown age:

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{beautier development and other resources}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

beautier successfully creates valid BEAST2 input files. Unlike BEAUti,
beascriptr allows for setting a fixed crown age.

beautier does not support the full functionality of BEAUti. Considering
the size, age and number of plugins, this would be close to impossible.
To compensate for this, an extensible software architecture is used.

beautier has minimal support for calling BEAST2 from within R and does
so for testing purposes.

beastscript has minimal support for parsing and interpreting BEAST2 output files,
for that the RBeast package is recommended.

The package is free and is available from the official R package archive at 
http://cran.r-project.org/src/contrib/PACKAGES.html\#beautier. 
beautier is licensed under the GNU General Public License.

@@

Scientists using beautier in a published paper should cite this
article. Users can additionally cite the beautier package 
directly. Citation information can be obtained by typing:

>>>>

BEAST2 \cite{bouckaert2014beast} is a popular Bayesian phylogenetics tool.
BEAST2 is bundled with the program called BEAUti \cite{drummond2012bayesian},
which  allows for a user-friendly way to create the
input files that BEAST2 needs. BEAUti is convenient to get started, yet
does not allow for the scripted use of BEAST2. For creating BEAST2 input
files from a script, \verb;beautier; is the R package facilitating this:
it creates a BEAST2 input files from an R function call.

@@

By creating BEAST2 input files in BEAUti, 
the desired output of \verb;beautier; was determined. 
The functionality of BEAUti is added gradually (and is still growing).

@@

Novel about \verb;beautier; is that it allows for specifying a fixed crown age:

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\verb;beautier; development and other resources}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\verb;beautier; successfully creates valid BEAST2 input files. Unlike BEAUti,
beascriptr allows for setting a fixed crown age.

\verb;beautier; does not support the full functionality of BEAUti. Considering
the size, age and number of plugins, this would be close to impossible.
To compensate for this, an extensible software architecture is used.

\verb;beautier; has minimal support for calling BEAST2 from within R and does
so for testing purposes.

\verb;beautier; has minimal support for parsing and interpreting BEAST2 output files,
for that the \verb;RBeast; package is recommended.

The package is free and is available from the official R package archive at 
http://cran.r-project.org/src/contrib/PACKAGES.html\#beautier. 
\verb;beautier; is licensed under the GNU General Public License.

@@

Scientists using \verb;beautier; in a published paper should cite this
article. Users can additionally cite the \verb;beautier; package 
directly. Citation information can be obtained by typing:
